---
title: 'Status of Petrale sole stock off the U.S. West Coast in 2023'
author:
  - name: 'Ian G. Taylor'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'Vladlena Gertseva'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
  - name: 'Nick Tolimieri'
    affiliations:
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'
        address: '2725 Montlake Boulevard East'
        city: 'Seattle, WA'
        state: 'WA'
        postal-code: '98112-2097'
date: today
lang: en 
keep-tex: true 
mainfont: 'Latin Modern Sans' 
cover: support_files/Petrale_sole.png
pdf-engine: lualatex
format: 
  pdf: 
    documentclass: scrartcl
    number-sections: true
    template-partials:
      - 'support_files/before-body.tex'
      - 'support_files/_titlepage.tex'
    include-in-header:
      - 'support_files/in-header.tex'
    include-after-body:
      text: |
        \newpage{}
        \printnoidxglossaries
    toc: true
    sansfont: 'Latin Modern Sans'
    lof: true
    lot: true
    titlepage-geometry: 
      - top=2in
      - bottom=1in
      - right=1in
      - left=1in
output-file: 'Petrale_sole_SAR_2023' 
params:
   office: 'NWFSC'
   species: 'Petrale sole'
   spp_latin: 'Eopsetta jordani'
   region: 'U.S. West Coast'
   nf: 'North fleet'
   sf: 'South fleet'
bibliography:  
  - asar_references.bib
---
```{r} 
#| label: 'output_and_quantities'
#| echo: false 
#| warning: false 
#| eval: true
# Call reference points and quantities below 
load(here::here("data", "petrale_output.rda"))
output <- petrale_output |>
  dplyr::mutate(estimate = as.numeric(estimate), 
    uncertainty = as.numeric(uncertainty)) 
 start_year <- output |> 
  dplyr::filter(era == 'time') |> 
  dplyr::summarise(min_year = min(year)) |> 
  dplyr::pull(min_year) |> 
  as.numeric() 
end_year <- output |> 
  dplyr::filter(era == 'time') |> 
  dplyr::summarise(max_year = max(year)) |> 
  dplyr::pull(max_year) |> 
  as.numeric() 
# subset output to remove quantities that are split by factor 
output2 <- output |> 
  dplyr::filter(is.na(season), 
    is.na(fleet), 
    is.na(sex), 
    is.na(area), 
    is.na(growth_pattern), 
    is.na(subseason), 
    is.na(age))
# terminal fishing mortality 
Fend <- output2 |> 
  dplyr::filter(c(label == 'fishing_mortality' & year == end_year) | c(label == 'terminal_fishing_mortality' & is.na(year))) |>
  dplyr::pull(estimate) |>
  unique()
# fishing mortality at msy 
# please change target if desired 
Ftarg <- output2 |>
  dplyr::filter(grepl('f_target', label) | grepl('f_msy', label) | c(grepl('fishing_mortality_msy', label) & is.na(year))) |>
  dplyr::pull(estimate)
# Terminal year F respective to F target 
F_Ftarg <- Fend / Ftarg
# terminal year biomass 
Bend <- output2 |>
  dplyr::filter(grepl('mature_biomass', label) | grepl('^biomass$', label),
    year == end_year) |>
  dplyr::pull(estimate)
# target biomass (msy) 
# please change target if desired 
Btarg <- output2 |>
  dplyr::filter(c(grepl('biomass', label) & grepl('target', label) & estimate >1) | label == 'biomass_msy') |>
  dplyr::pull(estimate)
# total catch in the last year 
total_catch <- output |> 
  dplyr::filter(grepl('^catch$', label), 
    year == end_year) |> 
  dplyr::group_by(year) |> 
  dplyr::summarise(total_catch  = sum(estimate)) |> 
  dplyr::ungroup() |> 
  dplyr::pull(total_catch) 
# total landings in the last year 
total_landings <- output |>
  dplyr::filter(grepl('landings_observed', label), year == end_year) |>
  dplyr::group_by(year) |>
  dplyr::summarise(total_land  = sum(estimate)) |>
  dplyr::ungroup() |>
  dplyr::pull(total_land)
# spawning biomass in the last year

SBend <- output2 |>
  dplyr::filter(grepl('spawning_biomass', label), year == end_year) |>
  dplyr::pull(estimate) |>
  unique()
# overall natural mortality or at age 
M <- output |>
  dplyr::filter(grepl('natural_mortality', label)) |>
  dplyr::pull(estimate)
# Biomass at msy 
# to change to another reference point, replace msy in the following lines with other label 
Bmsy <- output2 |>
  dplyr::filter(c(grepl('^biomass', label) & grepl('msy', label) & estimate >1) | grepl('^biomass_msy$', label)) |>
  dplyr::pull(estimate)
# target spawning biomass(msy) 
# please change target if desired 
SBmsy <- output2 |>
  dplyr::filter(c(grepl('spawning_biomass', label) & grepl('msy$', label) & estimate > 1) | label == 'spawning_biomass_msy$') |>
  dplyr::pull(estimate)
# steepness 
h <- output |> 
  dplyr::filter(grepl('steep', label)) |> 
  dplyr::pull(estimate)
# recruitment 
R0 <- output |> 
  dplyr::filter(grepl('R0$', label) | grepl('recruitment_virgin', label)) |> 
  dplyr::pull(estimate)
# female SB (placeholder)

``` 



{{< pagebreak >}}

## Disclaimer {.unnumbered .unlisted}

These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited or reproduced. They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce.

{{< pagebreak >}} 

Please cite this publication as: 

Taylor, I. G., Gertseva, V., and Tolimieri, N. 2023. Status of Petrale sole stock off the U.S. West Coast in 2023. Prepared by [COMMITTEE]. \pageref*{LastPage}{} pp.

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'executive_summary'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('01_executive_summary.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'introduction'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('02_introduction.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'data'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('03_data.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-configuration'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04a_assessment-configuration.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-results'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04b_assessment-results.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-sensitivity'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04c_assessment-sensitivity.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-benchmarks'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04d_assessment-benchmarks.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'assessment-projections'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('04e_assessment-projections.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'discussion'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('05_discussion.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'acknowledgments'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('06_acknowledgments.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'references'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('07_references.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'tables'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('08_tables.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'figures'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('09_figures.qmd', quiet = TRUE)
cat(a, sep = '\n')
```

 {{< pagebreak >}} 

```{r, results='asis'}
#| label: 'appendix'
#| eval: true
#| echo: false
#| warning: false
a <- knitr::knit_child('11_appendix.qmd', quiet = TRUE)
cat(a, sep = '\n')
```
